Detecting Cosmic Reionization using Bi-Spectrum Phase

### 2018-04-27 ResponseToEditor.txt

To the editorial staff:

We appreciate the referees' reports and their positive views on 
our work. We have responded to their comments, attached in a 
separate file.

We are attaching two versions of the Latex file. One is the 
updated ms.tex (ms.pdf). The other is ms_changes.tex (and 
ms_changes.pdf) and it contains all the changes highlighted in 
red.

@@

-----------------------------------------------------------------
  Figure   Aspect Ratio   Wide?   Word Equivalent
     1         1.54         No        117
     2         1.06         No        161
     3         3.73        Yes        200

WORD COUNT SUMMARY
    Note: Text word count excludes title, abstract, byline, PACS,
          receipt date, acknowledgments, and references.

              Text word count   4003
        Equations word equiv.    192
          Figures word equiv.    478
           Tables word equiv.      0
                              ------
                       TOTAL    4673 (Maximum length is 3750)
-----------------------------------------------------------------

Subsequently, we made substantial changes to reduce the length by
at least 1000 words including substantial changes to figure sizes. 
We confirmed this through "texcount" on the command line and 
carefully kept track of the word count at the time of initial 
submission (5 March 2018) as well as the trimmed one (12 March 
2018).

### 2018-04-27 ms_changes.tex
Update on Overleaf.

The redshift evolution of separability in $P_\nabla(k_\parallel)$ depends on relative strengths of the foreground and the EoR \HI\ signal. In the 175~MHz sub-band ($z\approx 7.1$), relative to the 150~MHz sub-band ($z\approx 8.5$), $\langle(\delta T_\textrm{b}^\textrm{H{\sc i}}(z))^2\rangle$ is weaker (see {\sc faint galaxies} model at $k=0.5$~Mpc$^{-1}$ in Fig.~2 of \cite{gre17b}) but the foreground synchrotron temperature is also fainter roughly by the same factor. Therefore, the separability of EoR \HI\ in $P_\nabla(k_\parallel)$ is roughly similar in the two sub-bands (Fig.~\ref{fig:cpdps-150}, \ref{fig:cpdps-175}). However, in the 125~MHz sub-band ($z\approx 10.4$), $\langle(\delta T_\textrm{b}^\textrm{H{\sc i}}(z))^2\rangle$ in the fiducial EoR model is fainter but the foregrounds are brighter, thereby significantly decreasing the spectral contrast between foregrounds and the EoR signal. Hence, a clear separability is not seen at $z\approx 10.4$ (Fig.~\ref{fig:cpdps-125}).

>>>>

The redshift evolution of separability in $P_\nabla(k_\parallel)$ depends on relative strengths of the foreground and the EoR \HI\ signal. In the 175~MHz sub-band ($z\approx 7.1$), relative to the 150~MHz sub-band ($z\approx 8.5$), $\langle(\delta T_\textrm{b}^\textrm{H{\sc i}}(z))^2\rangle$ is weaker (see {\sc faint galaxies} model at $k=0.5$~Mpc$^{-1}$ in Fig.~2 of \cite{gre17b}) but the foreground synchrotron temperature is also fainter roughly by the same factor. Therefore, the separability of EoR \HI\ in $P_\nabla(k_\parallel)$ is roughly similar in the two sub-bands. However, in the 125~MHz sub-band ($z\approx 10.4$), $\langle(\delta T_\textrm{b}^\textrm{H{\sc i}}(z))^2\rangle$ in the fiducial EoR model is fainter but the foregrounds are brighter, thereby significantly decreasing the spectral contrast between foregrounds and the EoR signal. Hence, a clear separability is not seen at $z\approx 10.4$.
